On the application of microwave acoustic resonant viral inactivation \thanks{I would be delighted to include any criticisms or comments anyone may have; preferably leave them on the GitHub issues page, or email therobotist@gmail.com, @0xDBFB7 on Twitter, or irc.0xDBFB7.com:6667 \#covid.}

### 2020-07-15 documents/paper.tex
Layer 0

That paragraph may cut an impressive figure; but recall that the rest of this paper

@@

To drive home this point, apparently the best-quality evidence available fulfills sham requirements [Vijayalaxmi 2006] provide in-vitro. They expose blood lymphocytes to pulse power  in precisely the regime required in this work; 8.2 GHz, 8 ns duration and 50 khz repetition rate, pulse power densities of 250,000 $W/m^2$\footnote{computed from average power / duty cycle}, for 2 hours, and find no genotoxicity. [Chemeris 2004] use 8.8 GHz, 180 ns pulse width, peak power 65,000 W , repetition rate 50 Hz, exposure duration 40 min, on frog etheyrocytes?

@@

How sensitive this research is, [Chemeris 2004] mention:\\

"The increase in DNA damage after exposure of cells to HPPP EMF shown in Table 2 was due to the temperature rise in the cell suspension by 3.5±0.1 ◦C. This was confirmed in sham-exposure experiments and experiments with incubation of cells for 40 min under the corresponding temperature conditions."\\

@@

This would seem to open an obvious avenue of optimization. If the virus is destroyed in tens of nanoseconds - essentially governed by instantaneous power. But tissue damage requires *energy deposition*.

Obviously, the solution is thus to turn the CW microwave signal into an effectively instantaneous pulse.

@@

However, [Oberoi 2012] find that they can detect a single E. Coli bacterium in 50 uL of broth via a microwave cavity. This is so unbelievable that we are inclined to look for methodological issues.

Frequency-domain measurements can be made with incredible precision; and there are many parameters by which virions could be discriminated; ring-up time of the resonance, excitation non-linearity, precise microwave spectroscopy, etc.

@@

Finally, there is one concern. It has been shown that virions can effect large-scale changes in the electric charges of their [].

Use of this technique will provide a selection bias towards immunity to electromagnetic fields, which could perhaps be effected by preferring extreme-sized mutants (shifting the resonance away from the applied field). We do not have the biological knowledge to know if this is plausible; it is simply worth mentioning.

>>>>

That paragraph may cut an impressive figure; but it hinges on all the rest of this paper being correct.

@@

To drive home this point, apparently the best-quality evidence available fulfills sham requirements [Vijayalaxmi 2006] provide in-vitro. They expose blood lymphocytes to pulse power  in precisely the regime required in this work; 8.2 GHz, 8 ns duration and 50 khz repetition rate, pulse power densities of 250,000 $\text{W/m}^2$\footnote{computed from average power / duty cycle}, average power 100 $\text{W/m}^2$ \footnote{the safety limit}, for 2 hours, finding no change in any of the measured quantities. [Chemeris 2004] use 8.8 GHz, 180 ns pulse width, peak power 65,000 W, repetition rate 50 Hz, exposure duration 40 min, on frog etheyrocytes, and find genotoxicity only from the temperature rise.

@@

How sensitive this research is, [Chemeris 2004] mention:

\begin{quote}

The increase in DNA damage after exposure of cells to HPPP EMF shown in Table 2 was due to the temperature rise in the cell suspension by $3.5\pm0.1^{\circ}  $C. This was confirmed in sham-exposure experiments and experiments with incubation of cells for 40 min under the corresponding temperature conditions."

@@

This would seem to open an obvious avenue of optimization. If the virus is destroyed in tens of nanoseconds via an electric field amplitude incidentally caused by an instantaneous power $\text{P}$, but tissue damage requires an energy deposition $\text{P}  \cdot  \text{dt}$, then we should minimize dt.\\

We thus turn the CW microwave signal into an effectively instantaneous pulse.

@@

However, [Oberoi 2012] find that - in controlled conditions - they can detect a single E. Coli bacterium in 50 uL of broth via a microwave cavity.

Of course, discriminating miniscule returns in free-space is not easy; but with precise knowledge of this resonance mode, it may become somewhat easier. Frequency-domain measurements can be made with incredible precision; and there are many parameters by which virions could be discriminated; ring-up time of the resonance, excitation non-linearity, etc.

@@

It has been shown that virions can effect large-scale changes in the electric charges of their [].

Use of this technique will provide a selection bias towards immunity to electromagnetic fields, which could perhaps be effected by preferring extreme-sized mutants (shifting the resonance away from the applied field).

We do not have the biological knowledge to know if this is plausible; it simply seemed worth mentioning.
